---
title: "EDH dataset cleaning and streamlining"
author: "Petra Hermankova"
date: "14/05/2020"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
---

```{r setup, echo=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE)
devtools::install_github("mplex/cedhar", subdir="pkg/sdam")
#install.packages("rjson")
#install.packages("tidyverse")
#install.packages("getPass")
#install.packages("formatR")

library(tidyverse)
library(tidytext)
library(dplyr)
library(stringr)
library(sdam)
library(rjson)
library(getPass)
library(formatR)
```

### Loading data

1. Input your sciencedata.dk username - type directly into the RStudio console
```{r, echo = FALSE }
user <- readline("your sciencedata username: ")
```

2. Make the request (you will be asked for password in a new pop-up window)

Sample data for testing (5000 inscriptions only)
```{r, echo = FALSE }
resp = request("EDH_clean_text_sample.json", path="/sharingin/648597@au.dk/SDAM_root/SDAM_data/EDH/", method="GET", cred=c(user, getPass("your sciencedata password: ")))
```


3. Make a list from the request and display the first six records (head)
```{r}
list_json <- fromJSON(resp)
EDH_tibble = as_tibble(list_json)
head(EDH_tibble)
```
# Cleaning `province_label` attribute

## 1. Creating new column `province_label_clean` stripped of all ?
```{r}
EDH_clean <- EDH_tibble %>% 
  mutate(province_label_clean = str_replace(EDH_tibble$province_label, pattern="\\?", replacement = ""))
```

## 2. Creating new column with `province_label_certainty` to record the uncertainty from `province_label` column
```{r}
EDH_clean$province_label_certainty <- ifelse(grepl("\\?", EDH_clean$province_label, ignore.case = T), "Uncertain", "Certain")
```
## 3. Checking the result
```{r}
number <- 8
EDH_clean$province_label[number]
EDH_clean$province_label_clean[number]
EDH_clean$province_label_certainty[number]
```

## 4. Checking there are no provinces with question mark
```{r}
EDH_clean$province_label_clean %>% 
  unique() %>% 
  sort(decreasing = FALSE)
```

# Cleaning `type_of_inscription` attribute

## 1. Creating new column `type_of_inscription` stripped of all ?
```{r}
EDH_clean <- EDH_clean %>% 
  mutate(type_of_inscription_clean = str_replace(EDH_tibble$type_of_inscription, pattern="\\?", replacement = ""))
```

## 2. Creating new column with `type_of_inscription_certainty` to record the uncertainty from `type_of_inscription` column
```{r}
EDH_clean$type_of_inscription_certainty <- ifelse(grepl("\\?", EDH_clean$type_of_inscription, ignore.case = T), "Uncertain", "Certain")
```
## 3. Checking the result
```{r}
number <- 20
EDH_clean$type_of_inscription[number]
EDH_clean$type_of_inscription_clean[number]
EDH_clean$type_of_inscription_certainty[number]
```

## 4. Checking there are no provinces with question mark
```{r}
EDH_clean$type_of_inscription_clean %>% 
  unique() %>% 
  sort(decreasing = FALSE)
`````


# Cleaning `material` attribute

## 1. Exploring the contents of the `material`column
```{r}
unique(EDH_clean$material)
```

## 2. Creating new column `material_clean` with main categories of the material based on Regula Expressions
```{r}
EDH_clean$material_clean <- ifelse(grepl("[Mm]ar[mor|ble]", EDH_clean$material, ignore.case = T), "Marble", 
ifelse(grepl("[Ll]imestone|[Kk]alkstein", EDH_clean$material, ignore.case = T), "Limestone", 
ifelse(grepl("[Aa]ndesit", EDH_clean$material, ignore.case = T), "Andesit",
ifelse(grepl("[Bb]asalt", EDH_clean$material, ignore.case = T), "Basalt", 
ifelse(grepl("[Bb]reccia", EDH_clean$material, ignore.case = T), "Breccia", 
ifelse(grepl("[Gg]neis", EDH_clean$material, ignore.case = T), "Gneiss", 
ifelse(grepl("[Gg]ranit", EDH_clean$material, ignore.case = T), "Granit", 
ifelse(grepl("[Qq]uartz", EDH_clean$material, ignore.case = T), "Quartz", 
ifelse(grepl("[Ss]andst[one|ein]", EDH_clean$material, ignore.case = T), "Sandstone", 
 ifelse(grepl("[Ss]chiefer|[Ss]late", EDH_clean$material, ignore.case = T), "Slate",       
ifelse(grepl("[Ss]teatit", EDH_clean$material, ignore.case = T), "Steatit", 
ifelse(grepl("[Tt]ravertin", EDH_clean$material, ignore.case = T), "Travertine", 
ifelse(grepl("[Tt]uff", EDH_clean$material, ignore.case = T), "Tuff",
ifelse(grepl("[Gg]old|[Bb]ronz|[Ss]il[vb]|[Bb]lei|[Ll]ead|[Ii]ron|[Ee]isen|[Bb]rass|[Mm]essing|[Zz]inn|[Tt]in", EDH_clean$material, ignore.case = T), "Metal",  
ifelse(grepl("[Kk]nochen|[Bb]one", EDH_clean$material, ignore.case = T), "Bone", 
ifelse(grepl("[Hh]olz|[Ww]ood", EDH_clean$material, ignore.case = T), "Wood", 
ifelse(grepl("[Gg]las", EDH_clean$material, ignore.case = T), "Glass", 
ifelse(grepl("[Tt]on|[Cc]lay|[Pp]ottery", EDH_clean$material, ignore.case = T), "Pottery", 
ifelse(grepl("[Rr]ock|[Gg]estein", EDH_clean$material, ignore.case = T), "Rock", 
ifelse(grepl("[Aa]labaster", EDH_clean$material, ignore.case = T), "Alabaster",
ifelse(grepl("NULL", EDH_clean$material, ignore.case = T), "NA",
                                          "Other")
                                   ))))))))))))))))))))
```

# Comparing the `material` with `material_clean` column
```{r}
number <- c(120:125)
EDH_clean$material[number]
EDH_clean$material_clean[number]
```

# Cleaning `height`, `width` and `depth` attributes

1. Cleaning the brackets
```{r}
EDH_clean <- EDH_clean %>% 
  mutate(height_cm = str_replace_all(EDH_clean$height, pattern = "[()]", "")) %>% 
  mutate(width_cm = str_replace_all(EDH_clean$width, pattern = "[()]", "")) %>% 
  mutate(depth_cm = str_replace_all(EDH_clean$depth, pattern = "[()]", ""))

```
2. Cleaning the text and converting as numeric
```{r}
EDH_clean$height_cm <- as.numeric(str_replace(EDH_clean$height_cm, pattern = " cm", ""))
EDH_clean$width_cm <- as.numeric(str_replace(EDH_clean$width_cm, pattern = " cm", ""))
EDH_clean$depth_cm <- as.numeric(str_replace(EDH_clean$depth_cm, pattern = " cm", ""))
```
## Testing the cleaning and conversion
```{r}
dim <- c(EDH_clean$height, EDH_clean$width, EDH_clean$depth)
dims <- c(EDH_clean$height_cm, EDH_clean$width_cm, EDH_clean$depth_cm)
interval <- c(100:103)

# automated checks
dim[interval]
dims[interval]

# testing if we can perform numeric operations
dims[1]+dims[2] 
```

# Cleaning `type_of_monument` attribute

## 1. Creating new column `type_of_monument_clean` stripped of all ?
```{r}
EDH_clean <- EDH_clean %>% 
  mutate(type_of_monument_clean = str_replace(EDH_tibble$type_of_monument, pattern="\\?", replacement = ""))
```
## 2. Creating new column with `province_label_certainty` to record the uncertainty from `province_label` column
```{r}
EDH_clean$type_of_monument_certainty <- ifelse(grepl("\\?", EDH_clean$type_of_monument, ignore.case = T), "Uncertain", "Certain")
```
## 3. Checking the result
```{r}
number <- 1333
EDH_clean$type_of_monument[number]
EDH_clean$type_of_monument_clean[number]
EDH_clean$type_of_monument_certainty[number]
```

# Cleaning `findspot_ancient` attribute

## 1. Cleaning `findspot_ancient` to a new column `findspot_ancient_clean`
```{r}
EDH_clean <- EDH_clean %>% 
  mutate(findspot_ancient_clean = str_replace(EDH_clean$findspot_ancient, pattern=", bei|, aus", replacement = ""))
EDH_clean$findspot_ancient_clean <- str_replace(EDH_clean$findspot_ancient_clean, pattern="\\?", replacement = "")
EDH_clean$findspot_ancient_clean <- str_replace(EDH_clean$findspot_ancient_clean, pattern=", inter", replacement = "")
EDH_clean$findspot_ancient_clean <- str_replace(EDH_clean$findspot_ancient_clean, pattern="(^[\\(])(.+)([\\)]$)", replacement = "\\2")
```

# Creating an index of localization certainty `findspot_ancient_certainty`
```{r}
EDH_clean$findspot_ancient_certainty <- ifelse(grepl(" bei| aus]", EDH_clean$findspot_ancient, ignore.case = T), "Estimated", 
ifelse(grepl("inter", EDH_clean$findspot_ancient, ignore.case = T), "In between",
ifelse(grepl("\\?", EDH_clean$findspot_ancient, ignore.case = T), "Uncertain",
ifelse(grepl("^\\(", EDH_clean$findspot_ancient, ignore.case = T), "Uncertain", 
ifelse(grepl("NULL", EDH_clean$findspot_ancient, ignore.case = T), "NULL", 
       "Certain" )))))
```

## Checking the results
```{r}
interval <- c(1:10)
EDH_clean$findspot_ancient[interval]
EDH_clean$findspot_ancient_clean[interval]
EDH_clean$findspot_ancient_certainty[interval]
```
### Checking the success rate of cleaning `findspo_ancient`
```{r}
cleaned_findspot <- unique(EDH_clean$findspot_ancient_clean) %>% 
  length()
original_findspot <- unique(EDH_clean$findspot_ancient) %>% 
  length()
cleaning_rate <- 100 - (cleaned_findspot /(original_findspot/100))
```

# Saving to Sciencedata
```{r}
EDH_cleaned_json <- rjson::toJSON(EDH_clean)
write(EDH_cleaned_json, file="EDH_cleaned_sample.json")
user <- readline("your sciencedata username: ")
request("EDH_cleaned_sample.json", path="/sharingout/648597@au.dk/SDAM_root/SDAM_data/EDH/", 
        method="PUT", cred=c(user, getPass("your sciencedata password: "))) 
```

